Of judges, aliens and total preorders

### 2021-02-27 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: removed reference to belief set
feat: some more text

\begin{frame}{Enriching Epistemic States}
    \begin{itemize}
        \item Additional structure of plausibility of worlds under new evidence $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
        \item Worlds are either supported by evidence or not $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
        \item Interval representing a world $(w^{+}, w^{-})$
    \end{itemize}
    \note{
        \begin{itemize}
            \item W+-
        \end{itemize}
    }
\end{frame}

\begin{frame}{$\leq$-faithful tpo}
    \begin{itemize}
        \item original tpo $\leq$ was an order over $W$
        \item additional structure $\preceq$ over new $W^{\pm}$
    \end{itemize}

@@

    \begin{itemize}
        \item $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$
        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
        \item $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
        \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
              \begin{itemize}
                  \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than Mary being the murderer"
                  \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".
              \end{itemize}
    \end{itemize}

@@

\section{Iterating: \texorpdfstring{$\preceq$}{tpo}-revision}
\note{
    \begin{itemize}
        \item Vorher: BM revisions operatoren definition, Revision der tpo am Beispiel
        \item Jetzt: Revision der neuen Struktur $\preceq$, ansonsten Problem mehrmaliger Revision nur "hochgeschoben"
        \item Jetzt: Ein möglicher konkreter Beispieloperator + Visualisierung
    \end{itemize}
}

\begin{frame}{A concrete operator}
    \begin{itemize}
        \item $p: W^{\pm} \mapsto \mathds{R}$
        \item $p(x^{-}) - p(x^{+}) = a > 0$
        \item $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
        \item Set $p$, for every $x^{\epsilon} \in W^{\pm}$, to:
    \end{itemize}

@@

@@

    \note{
        \begin{itemize}
            \item figure 7
        \end{itemize}
    }
\end{frame}

>>>>

\begin{frame}{Enriching Epistemic States}
    \begin{itemize}
        \item Additional structure $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
        \item "A bad day surfing is better than a good day working" \cite{booth2006bad}
        \item Worlds are either supported by evidence or not $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
        \item Interval representing a world $(w^{+}, w^{-})$
    \end{itemize}
    \note{
        \begin{itemize}
            \item Additional structure of plausibility of worlds under new evidence  W+-
            \item "A bad day surfing is better than a good day working" als idee das eine Welt sogar unter evidenz die sie nicht supported mehr plausibel bleiben kann, e.g. aliens tendenziell nicht so einfach zu glauben
        \end{itemize}
    }
\end{frame}

\begin{frame}{$\leq$-faithful tpo}
    \begin{itemize}
        \item original tpo $\leq$ was an order over $W$
        \item $\preceq$ over new $W^{\pm}$
    \end{itemize}

@@

    \begin{itemize}
        \item $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$
        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
        \item $min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
        \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
              \begin{itemize}
                  \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than Mary being the murderer"
                  \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".
              \end{itemize}
    \end{itemize}

@@

\section{Iterating: \texorpdfstring{$\preceq$}{tpo}-revision}
\note{
    \begin{itemize}
        \item Vorher: BM revisions operatoren definition, Revision der tpo am Beispiel
        \item Jetzt: Revision der neuen Struktur $\preceq$, ansonsten Problem mehrmaliger Revision nur "hochgeschoben"
        \item Jetzt: Ein möglicher konkreter Beispieloperator + Visualisierung
        \item Jetzt: Wie die Revision von Annahmen funktioniert für mehr als einen Input
    \end{itemize}
}

\begin{frame}{A concrete operator: Setup}
    \begin{itemize}
        \item Function p mapping worlds to real numbers: $p: W^{\pm} \mapsto \mathds{R}$
        \item Interval representing a world: $(p(x^{+}), p(x^{-}))$
        \item Distance between representations: $p(x^{-}) - p(x^{+}) = a > 0$
        \item Define a tpo from $p$: $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
    \end{itemize}

\begin{frame}{A concrete operator: Iteration}
    \begin{itemize}
        \item Choose initial $p$ so that $\preceq_{p} = \preceq$
        \item Revise $p$ by $\alpha$ to $p \ast \alpha$, for every $x^{\epsilon} \in W^{\pm}$:
    \end{itemize}

@@

    \begin{itemize}
        \item Define a revised tpo $\preceq_{p \ast \alpha}$ from $p \ast \alpha$: $x^{\epsilon} \preceq_{p \ast \alpha} y^{\delta} \textrm{ iff } (p \ast \alpha)(x^{\epsilon}) \leq (p \ast \alpha)(y^{\delta})$
    \end{itemize}

@@

    \note{
        \begin{itemize}
            \item figure 7
            \item maybe put the figure 5 from paper (original revision of <=) before this
            \item maybe put slides for complete example in here going from tpo to revision once, to revision twice
        \end{itemize}
    }
\end{frame}
